The \dealii Library, Version 9.0

### 2018-05-13 9.0/paper.tex
Fix a typo

\dealii has had a tutorial program (step-33) since 2007 that
demonstrates this technique based on the Trilinos Sacado \cite{Bartlett2006a} package, but
the functionality was not available pervasively throughout
deal.II.
This has changed with release 9.0 where support is given for differentiation
using a selection of ``white-listed'' libraries (namely ADOL-C \citep{Griewank1996a}
and Sacado) and a subset of their supported number types. Currently,
we offer support for the following cases:
\begin{itemize}
\item ADOL-C taped (n-differentiable),
\item ADOL-C tapeless (once differentiable),
\item Sacado dynamic forward (once differentiable),
\item Sacado reverse (once differentiable),
\item Sacado nested dynamic forward (twice differentiable), and
\item Sacado nested reverse and dynamic forward (twice differentiable).
\end{itemize}
In practice, this support means that these ADOL-C and Sacado data
types can be used in the \texttt{FEValues}, \texttt{FEValuesViews},
\texttt{Tensor}, \texttt{SymmetricTensor},
and related classes that are generally used to assemble linear systems
and right hand sides.
Given the updated capabilities of the library, there is now a dedicated module
that presents the AD compatibility and capabilities of the \dealii libraries.
Furthermore, the use of Sacado is now  demonstrated in a much more simplified
and transparent manner in an modernized version of an existing ``code gallery''
example \cite{Pelteret2016a}.

>>>>

\dealii has had a tutorial program (step-33) since 2007 that
demonstrates this technique based on the Trilinos Sacado \cite{Bartlett2006a} package, but
the functionality was not available pervasively throughout
deal.II.
This has changed with release 9.0 where support is given for differentiation
using a selection of ``white-listed'' libraries (namely ADOL-C \citep{Griewank1996a}
and Sacado) and a subset of their supported number types. Currently,
we offer support for the following cases:
\begin{itemize}
\item ADOL-C taped (n-differentiable),
\item ADOL-C tapeless (once differentiable),
\item Sacado dynamic forward (once differentiable),
\item Sacado reverse (once differentiable),
\item Sacado nested dynamic forward (twice differentiable), and
\item Sacado nested reverse and dynamic forward (twice differentiable).
\end{itemize}
In practice, this support means that these ADOL-C and Sacado data
types can be used in the \texttt{FEValues}, \texttt{FEValuesViews},
\texttt{Tensor}, \texttt{SymmetricTensor},
and related classes that are generally used to assemble linear systems
and right hand sides.
Given the updated capabilities of the library, there is now a dedicated module
that presents the AD compatibility and capabilities of the \dealii libraries.
Furthermore, the use of Sacado is now  demonstrated in a much more simplified
and transparent manner in a modernized version of an existing ``code gallery''
example \cite{Pelteret2016a}.
